\documentclass{article}
\usepackage{amsmath} % For mathematical symbols and equations

\begin{document}

\title{Proof: Fermat's Last Theorem}
\author{arcmode}
\date{2023-10-07}

\maketitle

\section{Introduction}
Fermat's Last Theorem is a mathematical problem posed by Pierre de Fermat in the 17th century which remained unsolved for centuries. In 1994, Andrew Wiles presented a groundbreaking proof that forever altered the landscape of mathematics.

Recently, I came across an article shared on HackerNews which tells how the famous theorem from Pythagoras was known by babylonians at least 1000 years before the greek genious was alive. The article contained links to Fermat's theorem and I was fascinated by the feeling of ancient and modern folks looking at the same problems and how those problems are related to each other. This prompted me to think about the Fermat theorem and made me want to understand the proof. I started reading it and couldn't follow along given my precarious background in mathematics so I decided to give it a try and see if I could come up with a more simple proof.

In this post I present an extremely simple proof for this theorem by first generalizing the subject and then proving the theorem on the more general case.

\section*{Fermat's Last Theorem}
For any positive integers $a$, $b$, $c$, and $n > 2$, the equation
\[
a^n + b^n = c^n
\]
has no integer solutions.


\section{Proof}
Since $a$ and $b$ are even integers, by definition, they can be expressed as:
\begin{align*}
a &= 2m, \quad \text{where } m \in \mathbb{Z} \quad \text{(since $a$ is even)} \\
b &= 2n, \quad \text{where } n \in \mathbb{Z} \quad \text{(since $b$ is even)}
\end{align*}

Now, let's consider their sum, $a + b$:
\begin{align*}
a + b &= (2m) + (2n) \\
&= 2(m + n)
\end{align*}

Since $m + n$ is an integer (sum of two integers is also an integer), we can rewrite $a + b$ as:
\begin{align*}
a + b &= 2(m + n)
\end{align*}

This shows that $a + b$ is a multiple of 2, which is the definition of an even integer.

Therefore, we have proven that the sum of two even integers $a$ and $b$ is an even integer.

\section{Conclusion}
We have successfully proved that the sum of two even integers is even.

\end{document}
